Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-05-15 RNARedPrint-Bioinfo2018.tex
Update on Overleaf.

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
             &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{Uniform} & \textbf{Improvement} \\\toprule
  Seeds      & 2str & 21.67 ($\pm$4.38) & 37.74 ($\pm$6.45) & 73\%\\
             & 3str & 18.09 ($\pm$3.98) & 30.49 ($\pm$5.41) & 71\%\\
             & 4str & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & PK60 & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & PK80 & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & 4str & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             \midrule

>>>>

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
             &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{Uniform} & \textbf{Improvement} \\\toprule
  Seeds      & 2str & 21.67 ($\pm$4.38) & 37.74 ($\pm$6.45) & 73\%\\
             & 3str & 18.09 ($\pm$3.98) & 30.49 ($\pm$5.41) & 71\%\\
             & 4str & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & PK60 & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & PK80 & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & LE80 & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             \midrule
